---
title: "Alcohol vs Seat choice"
author: "Sarah Castellon"
date: "October 1 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question 
Is there a difference between the alcohol consumed between the row  

##Method
we are predict alcohol consumption based on where you sit

$H_0$ there is no difference in the alcohol consumption based on where you site  
$H_A$ there is a difference in the alcohol consumption based on where you site

Alcohol is numerical and seat is categorical so we will use the Num ~ Cat file  

## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Box plot show that the higher level alcohol consumption of those seated in the back and decreases as you move to the middle and front seats.  

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The average of alcohol consumption in ounces for those seated in the back is 8.5, which is higher then the average of those in the middle who's alcohol consumption was 3.33 ounces and the front had the least amount of alcohol consumption with 1.79 ounces.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
P Value is .000116 which is lower then .05. Thus we reject the null hypothesis. 

```{r}
plot(TukeyHSD(model1))
```
  

The tukey show that the middle front has no difference where middle back and front back have a difference. 

## Conclusions
We conclude the that the alcohol consumption of those who are seated in the back were higher then those who sat in the middle or front. The numerical results show the average consumption of alcohol of those in the back was 8.5 where the middle was 3.3 and the front was 1.7. The P Value is .000116 which is lower then .05. so we reject the null hypothesis as there is a difference in the alcohol consumption based on where you are seated.


