---
title: "Alcohol vs Seat choice"
author: "Sarah Castellon"
date: "October 1 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question 
Is there a difference between the alcohol consumed between the row  

##Method
we are predict alcohol consumption based on where you sit

$H_0$ there is no difference in the alcohol consumption based on where you site  
$H_A$ there is a difference in the alcohol consumption based on where you site

Alcohol is numerical and seat is categorical so we will use the Num ~ Cat file  

## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Box plot show that the higher level alcohol consumption of those seated in the back and decreases as you move to the middle and front seats.  

## Numerical Summarys 

## Inferential Tests

## Conclusions


